---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scisorseqr

<!-- badges: start -->
<!-- badges: end -->

For any comparative (e.g. case-control) studies of alternative splicing,
scisorseqr is the one stop shop for analyzing single-cell long read data. The linux 
based package includes functions for barcode deconvolution from fastqs,
integration with long read alignment tools like STARlong and minimap2,
mapping and filtering of high confidence full-length spliced reads, and some
handy tools to conduct and visualize differential splicing analysis.

![scisorseqr workflow]('~/Documents/TilgnerLab/GitLab/spatialViz/www/scisorseqR_schematic.pdf'){width=65%}

## Installation

The easiest way to install scisorseqr is through [Github](https://github.com) with:

``` r
devtools::install_github('noush-joglekar/scisorseqr')
```

## Workflow

This is a basic example which shows you how to solve a common problem:

```{r example}
library(scisorseqr)
GetBarcodes('FastqFiles/','userInput/BarcodeCluster_Assignments', concatenate=TRUE, 
            filterReads=FALSE, numProcesses=24)
## basic example code
```


